Ensemble Stability of Biological Networks

### 2014-09-12 journal.tex
add table with graphs
move table to separate file

\pagebreak

% \begin{table}[h]
\begin{longtable}{ c || c | c | c | c }
\hline
matrix & connectivity & cycle number & \specialcell{probability of stability\\to perturbation} & probability of stability\\
\hline
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 0\\
0 & 0 & 1\\
\end{pmatrix}$ & 3 & 0 & 0.496 & 0.122\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 4 & 1 & 0.496 & 0.13\\
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 4 & 0 & 0.626 & 0.128\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 1 & 0.602 & 0.127\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 0\\
\end{pmatrix}$ & 5 & 2 & 0.496 & 0.122\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 0 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 2 & 0.405 & 0.061\\
$\begin{pmatrix}
0 & 1 & 0\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 1 & 0.429 & 0.081\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 5 & 1 & 0.597 & 0.129\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 0\\
\end{pmatrix}$ & 5 & 2 & 0.408 & 0.062\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 5 & 0 & 0.693 & 0.125\\
$\begin{pmatrix}
1 & 0 & 0\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 5 & 1 & 0.606 & 0.124\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 0\\
0 & 1 & 1\\
\end{pmatrix}$ & 5 & 0 & 0.705 & 0.131\\
$\begin{pmatrix}
0 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 2 & 0.578 & 0.115\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 0 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 3 & 0.489 & 0.085\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 2 & 0.548 & 0.091\\
$\begin{pmatrix}
0 & 1 & 0\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 2 & 0.493 & 0.087\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 0\\
1 & 1 & 1\\
\end{pmatrix}$ & 6 & 1 & 0.669 & 0.128\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 0\\
\end{pmatrix}$ & 6 & 3 & 0.474 & 0.086\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 0\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 2 & 0.587 & 0.12\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 6 & 1 & 0.656 & 0.121\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
0 & 0 & 1\\
\end{pmatrix}$ & 6 & 0 & 0.741 & 0.125\\
$\begin{pmatrix}
1 & 1 & 0\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 6 & 1 & 0.596 & 0.098\\
$\begin{pmatrix}
0 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 3 & 0.572 & 0.094\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 0 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 5 & 0.465 & 0.075\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 7 & 3 & 0.592 & 0.105\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
0 & 1 & 1\\
\end{pmatrix}$ & 7 & 1 & 0.713 & 0.122\\
$\begin{pmatrix}
1 & 0 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 7 & 2 & 0.642 & 0.125\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
1 & 0 & 1\\
\end{pmatrix}$ & 7 & 2 & 0.628 & 0.11\\
$\begin{pmatrix}
0 & 1 & 1\\
1 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 8 & 5 & 0.578 & 0.092\\
$\begin{pmatrix}
1 & 1 & 1\\
0 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 8 & 3 & 0.647 & 0.115\\
$\begin{pmatrix}
1 & 1 & 1\\
1 & 1 & 1\\
1 & 1 & 1\\
\end{pmatrix}$ & 9 & 5 & 0.635 & 0.11\\
\caption{{\bf Probability of stability under resampling and \emph{a priori} stability for three component systems estimated via Monte Carlo sampling.} All matrices not listed have $0$ probability of stability.}\label{tab:structstabmat3}
\end{longtable}
%
% \end{table}

>>>>

\newpage

\input{tablenographs}

\newpage

\input{tablewithgraphs}
